systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-04-28 paper/trunk/systemfit_summary.tex
several small mainly cosmetic changes (e.g. dashes)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@665 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\subsubsection*{Estimation methods}
In the future, we wish to include more sophisticated estimation
methods such as limited-information maximum likelihood (LIML),
full-information maximum likelihood (FIML), and generalized methods of
moments (GMM).

>>>>

\subsubsection*{Estimation methods}
In the future, we wish to include more sophisticated estimation
methods such as limited information maximum likelihood (LIML),
full information maximum likelihood (FIML), generalized methods of
moments (GMM) and spatial econometric methods.
